Progress Report on One Simulated Dataset

### 2023-10-06 Docs/ProgressReportSim.Rmd
calculated ISE and AUC

```{r}
# calcualte AUC
auc1 <- test_df %>%
  left_join(bind_rows(pred_list), by = c("id", "bin")) %>%
  filter(bin==sind) %>%
  mutate(window = cut(bin, breaks = seq(0, 1000, by = 200), include.lowest = T)) %>%
  select(Y, starts_with("pred"), window)

auc1 <- split(auc1, f = auc1$window)

tb_auc1 <- matrix(NA, 5, 4)

for(i in 2:4=5){

  this_lst <- auc1[i:5]

  for(j in seq_along(this_lst)){
     tb_auc[ ,i]

  }

  tb_auc1[(i+1):5, i]
}

>>>>

```{r}
# calcualte AUC
# FPCA eigenvalues
auc_df1 <- test_df %>%
  left_join(bind_rows(pred_list), by = c("id", "bin")) %>%
  filter(bin==sind) %>%
  mutate(window = cut(bin, breaks = seq(0, 1000, by = 200), include.lowest = T)) %>%
  select(Y, starts_with("pred"), window)

obs_track <- seq(200, 800, by = 200)
pred_window <- unique(auc_df1$window)
auc_mat <- matrix(NA, length(pred_window), length(obs_track))

for(j in seq_along(obs_track)){
  for(i in (j+1):5){
    this_Y <- auc_df1$Y[auc_df1$window==pred_window[i]]
    this_pred <- auc_df1[auc_df1$window==pred_window[i],
                         paste0("pred", j)]
    this_perf <- performance(prediction(this_pred, this_Y), measure = "auc")
    auc_mat[i ,j] <- this_perf@y.values[[1]]
  }
}
```

```{r}
# calcualte AUC
# FPCA eigenvalues
auc_df2 <- test_df %>%
  left_join(bind_rows(pred_list2), by = c("id", "bin")) %>%
  filter(bin==sind) %>%
  mutate(window = cut(bin, breaks = seq(0, 1000, by = 200), include.lowest = T)) %>%
  select(Y, starts_with("pred"), window)

auc_mat2 <- matrix(NA, length(pred_window), length(obs_track))

for(j in seq_along(obs_track)){
  for(i in (j+1):5){
    this_Y <- auc_df2$Y[auc_df2$window==pred_window[i]]
    this_pred <- auc_df2[auc_df2$window==pred_window[i],
                         paste0("pred", j)]
    this_perf <- performance(prediction(this_pred, this_Y), measure = "auc")
    auc_mat2[i ,j] <- this_perf@y.values[[1]]
  }
}
```

auc <- cbind(auc_mat, auc_mat2)
rownames(auc) <- unique(auc_df1$window)
colnames(auc) <-c(rep(seq(200, 800, by =200), 2))
auc %>%
  kable(digits = 3, table.attr = "style = \"color: black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" "= 1, "FPCA eigenvalues" = 4, "Debiased eigenvalues" = 4)) %>%
  add_header_above(c(" "=1, "Maximum observation time" = 8))
```
